\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Introduction and Application of Real Time Databases}

\author{\IEEEauthorblockN{Ryan Goodwin}
\IEEEauthorblockA{
rgoodwin@smu.edu}
\and
\IEEEauthorblockN{Karl Jurek}
\IEEEauthorblockA{
kjurek@smu.edu}
\and
\IEEEauthorblockN{Travis Daun}
\IEEEauthorblockA{
tdaun@smu.edu}
}

\maketitle

\begin{abstract}
This document outlines our research proposal on real-time database systems.  
\end{abstract}

%\begin{IEEEkeywords}
%component, formatting, style, styling, insert
%\end{IEEEkeywords}

\section{Problem Statement}
Real-time database system is a database system where timing constraints are associated with transactions and data have specific time intervals for which data is valid. The groups goal will be to introduce the concepts and constraints associated with the implementation of real-time databases in real-world applications

\section{Research Methodology}
A survey-paper approach to real-time database applications will be utilized in an effort to gain in-depth understanding of real-time database implementation and applications. We will discuss in detail the use and implementation of real-time databases in various applications.\\
\indent Firebase, Google's NoSQL cloud database, will be discussed as a concrete example of an open-source, real-time, cloud-hosted database.

\section{Previous work related to the problem}
There are numerous academic papers that we identified related to the implementation and employment of real-time databases for various applications. The reference section of this paper lists the papers we have identified through our preliminary literature review (~\cite{a1}, ~\cite{a2}, ~\cite{a3}, ~\cite{a4}, ~\cite{a7}) . In addition to academic papers, whole textbooks have been written which provide background on real-time database concepts, architecture, and implementation (~\cite{a5}, ~\cite{a6}).\\
\indent Through the team's preliminary research we have also identified numerous on-line sources of information related to real-time databases. Most notably, Google hosts a cache of documentation for their Firebase Realtime Database at \texttt{https://firebase.google.com/docs/database/} which the team intends to use to discuss how real-time databases are used with a concrete example showing how Firebase is utilized in an actual application.

\section{Research plan and schedule}
\subsection{Team Meetings}
Wednesdays at 8:30 P.M. EST  and Saturdays at 8 A.M. EST via Zoom. Scheduled and invites coordinated by Karl.
\subsection{Communication Tools}
\paragraph{Slack} 
\begin{center}
Channel: 7330TermProject\\
\texttt{7330termproject.slack.com}\\
\end{center}
\paragraph{Github} 
\begin{center}
Repository: MSDS\_7730\_Project\_TD\_RG\_KJ
\texttt{https://github.com/}\\
 \texttt{kjurekSMU/MSDS\_7730\_Project\_TD\_RG\_KJ}
\end{center} 

\subsection{Project Milestones}
\begin{tabular}{|c|c|}
\hline
Week 4 & Submit Project Proposal\\
\textbf{June 2, 2019} & \textbf{2DS Submission}\\
\hline
Weeks 5-6 & Establish a Github Repository\\
                   & Continue survey-paper \\
                   & research into RTDBs.\\
\hline
Week 7 & Prepare Initial Presentation\\
\textbf{June 25, 2019} &  \textbf{Class Presentation}\\
\hline
Week 8-9 & Research into Google Firebase \\
				& as a concrete example of RTDBs.\\
				&  Explore possible implementation\\ 
				& of Firebase.\\
\hline
Week 10  & Project Draft I\\
\textbf{July 14, 2019} & \textbf{2DS Submission}\\
\hline
Week 11-12 &  Finalize research.\\
				  & Prepare research for final \\
				  & presentation and final paper.\\
\hline
Week 13-14 & Final presentation ready.\\
\textbf{August 6, 2019} & textbf{Class Presentation}\\
August 13, 2019 & \\
\hline
Week 15 & Final Paper ready to submit \\
\textbf{August 18, 2019} & \textbf{2DS Submission}\\
\hline
\end{tabular}

\section{Resources needed}
The team will utilize the SMU library's digital collection of academic articles to perform our survey research. In addition to our survey research, we will be utilizing Google's documentation for Firebase to develop a concrete example of how real-time databases are implemented and employed. The team does not foresee any resource limitations that would need to be addressed before proceeding with this research topic.

\section{Important pieces we don’t yet have access to}
As discussed, the team does not foresee any obstacles to obtaining the information or resources we will need to complete this research project.

\begin{thebibliography}{00}
\bibitem{a1} Han, Song et al. “Adaptive Co-Scheduling for Periodic Application and Update Transactions in Real-Time Database Systems.” The Journal of Systems \& Software 85.8 (2012): 1729–1743.
\bibitem{a2} Sun, Q et al. “Implementation of Massive Real-Time Database System Using Network Sensors and Sector Operation.” Sensors \& Transducers 174.7 (2014): 123–128.
\bibitem{a3} Jian-Feng, Lu, Chun-Yi, Wang, and Jie, Hu. “A High Performance Data Storage Method for Embedded Linux Real-Time Database in Power Systems.” Energy Procedia 16.PB (2012): 883–888.
\bibitem{a4} S. Samaiya and M. Agarwal, "Real time database management system," 2018 2nd International Conference on Inventive Systems and Control (ICISC), Coimbatore, 2018, pp. 903-908.
\bibitem{a5} Lam, Kam-Yiu., and Kuo, Tei-Wei. Real-Time Database Systems Architecture and Techniques / Edited by Kam-Yiu Lam, Tei-Wei Kuo. Boston, MA: Springer US, 2002. 
\bibitem{a6} RTDB: A Memory Resident Real-Time Object Database. United States. Dept. of Energy. Office of Energy Research, 2003
\bibitem{a7} Huang, K., Zhang, J., \& Yao, J. (2012). Exploration on the application of real-time database in ship electronic information system. Applied Mechanics and Materials, 263-266, 1414. 
\end{thebibliography}

\end{document}
